Transfer learning between Sentinel-1 acquisition modes enhances \\ the few-shot segmentation of natural oil slicks in the Arctic

### 2025-04-09 latex/manuscript.tex
preprint +gitignore

% The paper headers
% \markboth{\LaTeX\ PDF, IEEE GEOSCIENCE AND REMOTE SENSING LETTERS,~Vol.~XX, No.~Y, <Month>~2025}%
\markboth{Vadnais \MakeLowercase{\textit{et al.}}: EarthArXiv preprint, submittedApril 2025}
{Shell \MakeLowercase{\textit{Vadnais et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}

>>>>

% The paper headers
% \markboth{\LaTeX\ PDF, IEEE GEOSCIENCE AND REMOTE SENSING LETTERS,~Vol.~XX, No.~Y, <Month>~2025}%
\markboth{Vadnais \MakeLowercase{\textit{et al.}}: Preprint, April 2025}
{Shell \MakeLowercase{\textit{Vadnais et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}
